Supervision

### 2025-08-01 done.qmd
update

@@

June 16-18th: Panel DPR on DPR at International Conference on the Science of Science and Innovation ([ICSSI](https://icssi.org/)), Copenhagen

@@

@@

>>>>

2025-07-31 Published (late!) the [showcase for this year's class of PSY6422 Data Analysis and Visualisation](https://tomstafford.github.io/psy6422/class-of-2025.html) (check out previous year's showcases on [the course pages](https://tomstafford.github.io/psy6422))

@@

June 16-18th: Panel DPR on DPR at International Conference on the Science of Science and Innovation ([ICSSI](https://icssi.org/)), Copenhagen. Here's me and Anders Smith from Villum Fonden

<img src="images/icssi2025.jpg" height = 400>

@@

May 2025: Launch of the [Editors and Publishers Network](https://sheffield.ac.uk/openresearch/home/editors-and-publishers-network) at the University of Sheffield, following the event I convened in 2024.

2025-05-21 Final of our 2024-25 [AFIRE Funder Forum](https://researchonresearch.org/afire-funders-forum/) series; showcasing experiments by research funders. Talk recordings are on the website, as well as the [RoRI YouTube channel](https://www.youtube.com/@researchonresearchinstitut6175).

April 2025: Attended [Fostering Accountability for the Integrity of Research Studies (FAIRS)](https://www.sjcfairsmeeting.com/), St John's College, Oxford

@@

# 2022

Probably I did other things this year, but the only thing I can find a note of is

2022-03-09 Released code for making your own ['hybrid images'](https://github.com/tomstafford/hybridimages). They look different from different distances (vision science people: it is about putting different image information into different spatial frequencies)

<img src="images/2022-03-29hybrid.jpg" height = 400>

### 2025-08-01 supervision.qmd
update

@@

# Previous supervision and examining

>>>>

- [Anna Butters](https://scholar.google.com/citations?user=8mKDLWQAAAAJ&hl=en&oi=ao) (2024 -- 2026) on [Distributed Peer Review at the Volkswagen Foundation](https://researchonresearch.org/volkswagen-distributed-peer-review/)

@@

### External

- [Olha Guley](http://www.institutnicod.org/membres/etudiant-e-s/doctorant-e-s/guley-olha/?lang=fr) (2023 - ) Institut Jean Nicod, CNRS, Paris.

# Alumni! (Previous supervision and examining)
